The Practical Application of Computerised Multistage Tests

### 2021-03-02 article.Rmd
Removed theta character from ggplot as it causes warnings

```{r}
itemNo <- 7
itemID <- str_extract(rownames(df_difficulties)[itemNo], "Item\\d+")
itemDifficulty <- df_difficulties[itemNo]
itemPlot <- data.frame(plot(raschmodel, type = "ICC", items = itemNo, plot = FALSE))
colnames(itemPlot) <- c('theta', 'probability')
ggplot(itemPlot, aes(x=theta, y=probability)) + 
  geom_line() +
  labs(title="Item Characteristic Curve", x="θ", y="P(X=1)")
```
In this example we see the item characteristic curve (ICC) for `r itemID` with difficulty $b$ = `r itemDifficulty`.

@@

```{r Stage 1 MCC}
moduleA1_items <- which(colnames(dfTrial) %in% colnames(dfModuleAItems))
plotData <- trueScoreSummary(plot(raschmodel, 
                                  type = "ICC", 
                                  items = moduleA1_items, plot = FALSE), 
                             "A")
ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="θ", y="True Score")
```
You can read this off such that a candidate who scores 9 in module A would have an estimated ability score, or $\hat{\theta}$, of approximately 1.92.

@@

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="θ", y="True Score")
```
A problem we can see already here is that these curves look too straight - ideally there should be a nice sigmoid shape to them. These MCCs have a low information content - in other words they are not very discriminating. We may want to move some items between modules, or reject items that have poor discrimination.

@@

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="θ", y="True Score")
```
This is already showing us something a little weird. Our D (very easy) module is actually a little bit more difficult than our F (moderately hard) module at the top end of the scale. And the E (moderately easy) module is more difficult than the G (very hard) module. All of the modules are quite similar in terms of difficulty (the MCCs are quite close to each other), and moreover the lines are quite flat - there is little discrimination between them. We'll see how this can be expressed more obviously in the next section.

@@

# plot the theta/true score curve
ggplot(df_moduleA_TS, aes(x = theta, y = trueScore)) +
  geom_line(color = "red", linetype="dashed") +
  geom_point(data = df_gA, aes(x = theta, y = trueScore)) +
  scale_x_continuous(name="θ", limits=c(-4, 4)) +
  scale_y_continuous(name="True Score", limits=c(0, 12), 
                     minor_breaks = NULL, n.breaks = 12)
```
We can see that it is a good fit, both in the middle of the range, and importantly at the upper and lower bounds.

@@

```{r Item Information Function}
itemNo <- 7
itemID <- str_extract(rownames(df_difficulties)[itemNo], "Item\\d+")
itemDifficulty <- df_difficulties[itemNo]
itemPlot <- data.frame(plot(raschmodel, type = "IIC", items = itemNo, plot = FALSE))
colnames(itemPlot) <- c('theta', 'information')
ggplot(itemPlot, aes(x=theta, y=information)) + 
  geom_line() +
  labs(title="Item Information Function", x="θ", y="I(θ)")
```

@@

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Information Function", x="θ", y="I(θ)") +
  geom_vline(xintercept = cutTheta, linetype="dotted")

>>>>

```{r}
itemNo <- 7
itemID <- str_extract(rownames(df_difficulties)[itemNo], "Item\\d+")
itemDifficulty <- df_difficulties[itemNo]
itemPlot <- data.frame(plot(raschmodel, type = "ICC", items = itemNo, plot = FALSE))
colnames(itemPlot) <- c('theta', 'probability')
ggplot(itemPlot, aes(x=theta, y=probability)) + 
  geom_line() +
  labs(title="Item Characteristic Curve", x="theta", y="P(X=1)")
```
In this example we see the item characteristic curve (ICC) for `r itemID` with difficulty $b$ = `r itemDifficulty`.

@@

```{r Stage 1 MCC}
moduleA1_items <- which(colnames(dfTrial) %in% colnames(dfModuleAItems))
plotData <- trueScoreSummary(plot(raschmodel, 
                                  type = "ICC", 
                                  items = moduleA1_items, plot = FALSE), 
                             "A")
ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```
You can read this off such that a candidate who scores 9 in module A would have an estimated ability score, or $\hat{\theta}$, of approximately 1.92.

@@

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```
A problem we can see already here is that these curves look too straight - ideally there should be a nice sigmoid shape to them. These MCCs have a low information content - in other words they are not very discriminating. We may want to move some items between modules, or reject items that have poor discrimination.

@@

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="theta", y="True Score")
```
This is already showing us something a little weird. Our D (very easy) module is actually a little bit more difficult than our F (moderately hard) module at the top end of the scale. And the E (moderately easy) module is more difficult than the G (very hard) module. All of the modules are quite similar in terms of difficulty (the MCCs are quite close to each other), and moreover the lines are quite flat - there is little discrimination between them. We'll see how this can be expressed more obviously in the next section.

@@

# plot the theta/true score curve
ggplot(df_moduleA_TS, aes(x = theta, y = trueScore)) +
  geom_line(color = "red", linetype="dashed") +
  geom_point(data = df_gA, aes(x = theta, y = trueScore)) +
  scale_x_continuous(name="theta", limits=c(-4, 4)) +
  scale_y_continuous(name="True Score", limits=c(0, 12), 
                     minor_breaks = NULL, n.breaks = 12)
```
We can see that it is a good fit, both in the middle of the range, and importantly at the upper and lower bounds.

@@

```{r Item Information Function}
itemNo <- 7
itemID <- str_extract(rownames(df_difficulties)[itemNo], "Item\\d+")
itemDifficulty <- df_difficulties[itemNo]
itemPlot <- data.frame(plot(raschmodel, type = "IIC", items = itemNo, plot = FALSE))
colnames(itemPlot) <- c('theta', 'information')
ggplot(itemPlot, aes(x=theta, y=information)) + 
  geom_line() +
  labs(title="Item Information Function", x="theta", y="I(theta)")
```

@@

ggplot(plotData, aes(x=theta, y=information)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Information Function", x="theta", y="I(theta)") +
  geom_vline(xintercept = cutTheta, linetype="dotted")
